---
title: "Comparing Validation Results of Different CDH Installations"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Challenge

A customer want's to upgrade to a next version of the Uniser Customer Data Hub.
Such an upgrade usually includes new versions of Post, reference tables, 
convertName and CDH itself.

Since there are so many changes involved with such an upgrade, we want to be 
sure that the actual results created by such are an installation are at least 
of the same quality than in the previous or current software stack. We may also 
want to provide such evidence to the customer who wants to perform the upgrade.

## Approach

Since the validation results are created by Uniserv components, the idea was to 
explicitly NOT use any existing Uniserv software. However using software from
any of our competitors is of course a no-go as well. So we decided to perform 
the comparison by solely using **publicly available open-source software**.

Considering the highly customizable data model of CDH which allows for customer
specific data models, the appraoch must be flexible to analyse such differences
and to adapt the model accordingly. Therefore we followed an **exploratory data 
analysis** approach.

Finally we wanted to have something which allows us to *publish* the results in
different ways (a presentation or reports in PDF or Word or whatever) according
to the specific needs of the analysis - with **minimal effort**.

## How did we do it?

We have decided to use **R** to perform the comparison for the following 
reasons:

- R is open source (GPL-2|GPL-3)
- R is an object-oriented interactive language which is perfectly suited for 
analyzing and processing data step by step
- R provides out-of-the-box functionality to create data analysis reports (this 
presentation is created using so called R markdown)

For further reading go to
<http://www.nytimes.com/2009/01/07/technology/business-computing/07program.html>

## So what did we do?

The first question was: where do we get the data from? Since the analysis was
done in the context of a CDH project, we decided to use the **CSV export feature
provided by CDH**.

Next we loaded these exports into R and started analyzing. During the analysis
we found out that we forgot to ask the most important question: what are we 
looking for or what are our KPIs we want to create? Luckily R is perfectly 
suited to go into various directions and to **explore** the data as you go.

At the end we *wrote* the report (this presentation) about our findings.

And this is the result:

## Comparing CDH 15.4 and 16.1

Golden records and member records in both CDH versions:

```{r}
#plot(x)
```


## End

## Stuff

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

